Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-04-19 main.tex
:pencil: Update manuscript
:pencil: Update notations

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength. To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency. This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS. Considering energy harvester nonlinearity and practical transceiving strategies, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT). This non-convex problem is then solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is designed by the Geometric Programming (GP) technique. Since the computational complexity of the GP algorithm scales exponentially with the number of subbands, we also propose two closed-form adaptive waveform schemes to facilitate practical SWIPT implementation. Simulation results show considerable R-E gain over benchmark schemes and demonstrate the importance of accounting harvester nonlinearity in the passive beamforming design.
	\end{abstract}

@@

			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints and solve each boundary point by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT). For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity. For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS phase shift by a relax-then-extract method. Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique. The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.

			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation. To cooperate with the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS. The performances of both low-complexity designs are proved close to the BCD algorithm under different configurations.

			\emph{Fourth}, we provide numerical results to evaluate the performance of the proposed algorithms. It is concluded that 1) the proposed BCD algorithm always converges to local optimal points, 2) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 6) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 7) at different R-E points, the optimal IRS reflection coefficients coincide for narrowband SWIPT but differ for broadband SWIPT, 8) the proposed algorithms are robust to practical limitations as inaccurate cascaded CSIT and finite IRS reflection states.

@@

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\mathbb{C}^{x \times y}$ denotes the subspace spanned by complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ denote respectively the argument, rank, trace, and a square matrix with input elements on the main diagonal. $\boldsymbol{S} \succeq 0$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation with respect to random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ denote respectively the stationary value and the value at iteration $i$.
		\end{subsection}
	\end{section}

@@

		\begin{subsection}{Reflection Pattern and Composite Channel}
			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances. IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and its reflection coefficient is defined as
			\begin{equation}
				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l}
			\end{equation}
			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude~\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$. This paper sticks to the commonest and simplest IRS model where the reflection amplitude is always assumed unit to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift. We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector~\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.

@@

			Rectifiers consist of nonlinear components like diode and capacitor to produce DC output and store energy \cite{Pinuela2013}. Consider a simplified rectifier model in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function \footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage). With a slight abuse of notation, we refer to $z$ as the average output DC current in this paper. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$. However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior. For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}. Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear terms of the output DC current. Inspired by \cite{Huang2017}, we further stack $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and define $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$. As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}^{M \times M}$. Hence, the components of $z$ reduce to \eqref{eq:y_I2} -- \eqref{eq:y_P4}.

@@

			\begin{figure*}[!b]
				\hrule
				\begin{flalign}
					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),&&\label{eq:z_expand}
				\end{flalign}
				\begin{flalign}
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},&&\label{eq:y_I2}\\
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,&&\label{eq:y_I4}
				\end{flalign}
				\begin{flalign}
					\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},&&\label{eq:y_P2}\\
					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.&&\label{eq:y_P4}
				\end{flalign}
			\end{figure*}
		\end{subsection}

@@

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize each R-E boundary point through a current maximization problem subject to transmit power, IRS magnitude, and rate constraint as
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}

		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}. To obtain a feasible solution, we propose a BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.

@@

		\begin{table*}[!t]
			\caption{The maximum value of $1-\nu$ of all R-E samples over all tested channel realizations for BCD and LC-BCD algorithms}
			\label{ta:eigen_ratio}
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
				\hline
				\multicolumn{2}{|c|}{\multirow{2}{*}{}} & \multicolumn{3}{c|}{$M$} & \multicolumn{3}{c|}{$N$} & \multicolumn{3}{c|}{$L$} & \multicolumn{2}{c|}{$B$} \\ \cline{3-13}
				\multicolumn{2}{|c|}{} & \num{1} & \num{2} & \num{4} & \num{1} & \num{4} & \num{16} & \num{20} & \num{40} & \num{80} & \SI{1}{\MHz} & \SI{10}{\MHz} \\ \hline
				$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
				$[\times \num{e-16}]$ & LC-BCD & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
			\end{tabular}
		\end{table*}

		We first provide numerical proof on the rank-\num{1} property of $\boldsymbol{\Phi}$ thus the local optimality of Algorithm~\ref{al:sca}, \ref{al:bcd} and \ref{al:lc}. To see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$. Since $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$. For all intermediate $\boldsymbol{\Phi}$ achieved by Algorithm~\ref{al:sca}, Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ of \num{20} R-E samples over \num{300} tested channel realizations for both BCD algorithms. With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations. It suggests that the rank constraint \ref{co:irs_rank} can be relaxed, the phase shift $\boldsymbol{\phi}$ can be extracted by eigen decomposition without performance loss, and Algorithm~\ref{al:sca}, \ref{al:bcd} and \ref{al:lc} converge to local optimal points.

>>>>

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength. To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency. This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS. Considering energy harvester nonlinearity and practical transceiving strategies, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT). This non-convex problem is then solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is retrieved by the Geometric Programming (GP) technique. Since the computational complexity of the GP algorithm scales exponentially with the number of subbands, we also propose two closed-form adaptive waveform schemes to facilitate practical SWIPT implementation. Simulation results demonstrate that the proposed algorithms bring considerable R-E gains and are robust to CSIT inaccuracy and finite IRS reflection states. Results also emphasize the importance of accounting harvester nonlinearity in the passive beamforming design.
	\end{abstract}

@@

			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints and solve each boundary point by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT). For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity. For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS phase shift by a relax-then-extract method, where the performance loss by rank relaxation is proved negligible. Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique. The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.

			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation. To cooperate with the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS. The proposed low-complexity designs achieve near-optimal R-E performance under different configurations.

			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms. It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) at different R-E points, the optimal IRS reflection coefficients coincide for narrowband SWIPT but differ for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.

@@

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $\boldsymbol{0}$ denotes zero vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $j$ denotes the imaginary unit. $\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denotes the subspace spanned respectively by real and complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector as the main diagonal of the input matrix. $\boldsymbol{x} \succeq \boldsymbol{0}$ means every element of $\boldsymbol{x}$ is nonnegative, and $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation with respect to random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ denote respectively the stationary value and the value at iteration $i$.
		\end{subsection}
	\end{section}

@@

		\begin{subsection}{Reflection Pattern and Composite Channel}
			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances. IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and its reflection coefficient is defined as
			\begin{equation}
				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l}
			\end{equation}
			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$. This paper sticks to the commonest and simplest IRS model where the reflection amplitude is always assumed unit to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift. We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.

@@

			Rectifiers consist of nonlinear components like diode and capacitor to produce DC output and store energy \cite{Pinuela2013}. Consider a simplified rectifier model in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage). With a slight abuse of notation, we refer to $z$ as the average output DC current in this paper. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$. However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior. For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}. Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear terms of the output DC current. Inspired by \cite{Huang2017}, we further stack $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and define $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$. As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}^{M \times M}$. Hence, the components of $z$ reduce to \eqref{eq:y_I2} -- \eqref{eq:y_P4}.

@@

			\begin{figure*}[!b]
				\hrule
				\begin{flalign}
					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).&&\label{eq:z_expand}
				\end{flalign}
				\begin{flalign}
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},&&\label{eq:y_I2}\\
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,&&\label{eq:y_I4}
				\end{flalign}
				\begin{flalign}
					\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},&&\label{eq:y_P2}\\
					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.&&\label{eq:y_P4}
				\end{flalign}
			\end{figure*}
		\end{subsection}

@@

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and IRS magnitude constraints as
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}

		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}. To obtain a feasible solution, we propose a suboptimal BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.

@@
